Use of general purpose graphical processing units with MODFLOW

### 2012-09-16 GW20120518-0099-r01.tex
Revisions to document based on cost center review

\hspace{15pt}Kernels are blocks of code which are executed only on the GPGPU.  When the code is compiled, the compiler is instructed to use the API functions and routines to resolve the kernel block of code into GPGPU instructions. The kernels executed by the UPCG solver on the GPGPU are the CUDA-enable BLAS operations in the preconditioned conjugate gradient algorithm.\\ \color{black}}}
\bigskip

@@

A GPGPU is a set of streaming multiprocessors (SM), each having many CUDA cores (CC); each CC is capable of executing many threads simultaneously. This nested architecture gives rises to the massively parallel capability of GPGPUs.

\hspace{15pt}The total number of threads required to is a CUDA grid. A CUDA grid is composed of one or more blocks that are executed on one or more SM. All threads in a block run on the same SM with a dimension equal to the total number of times the kernel is applied. Each CUDA grid is . For increased throughput, threads within a block are further split into warps, which is the maximum number of threads that are managed and processed simultaneously on each CC. Multiple warps execute one after another to complete block processing of the kernel. All CCs within a SM execute the kernel concurrently, which results in massively parallel processing potential. GPGPU architecture and kernel execution are shown graphically in \textbf{figure~\ref{FigParallel}}.

>>>>

\hspace{15pt}Kernels are blocks of code which are executed only on the GPGPU.  When the code is compiled, the compiler is instructed to use the API functions and routines to resolve the kernel block of code into GPGPU instructions. The kernels executed by the UPCG solver on the GPGPU are the CUDA-enabled BLAS operations in the preconditioned conjugate gradient algorithm.\\ \color{black}}}
\bigskip

@@

A GPGPU is a set of streaming multiprocessors (SM), each having many CUDA cores (CC); each SM is capable of executing many threads simultaneously. This nested architecture gives rises to the massively parallel capability of GPGPUs.

\hspace{15pt}Each kernel launches a grid of threads composed of one or more blocks of grouped threads. The number of blocks in a grid is determined by the size of the kernel data being processed or the number of SM. The total number of threads in a grid is equal to the number of threads per block times the number of blocks. CCs on each SM can run one or more blocks but blocks are restricted to a single CC. Threads within a block are further grouped into warps, which is the maximum number of threads that are managed and processed simultaneously in each block. Multiple warps execute one after another to complete block processing of the kernel. GPGPU architecture and kernel execution are shown graphically in \textbf{figure~\ref{FigParallel}}.
